Sulfur Dioxide on Water's Surface

### 2011-03-19 Background.tex
wrote the conclusions, added some material in the density results.

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/density/Density+SurfaceLocation-flawed.png}
		\caption{Density profiles of \wat~(dashed) and\suldiox~(red) from a 10 ns simulation of the neat-water system with a single sulfur dioxide. The \wat~density profile was fit using a hyperbolic tangent function to extract location and width data. The location of the outter \wat~monolayer was calculated, and the corresponding location distribution (blue) is also plotted. Long simulations of liquid slabs result in drift of the slab location, and the consequent broadening of the water density profile if the surface location is not determined repeatedly throughout the simulation.}
		\label{fig:density-flaw}
	\end{center}
\end{figure}

### 2011-03-19 DensityResults.tex
wrote the conclusions, added some material in the density results.

In the neat-water \suldiox~distribution, $\mu=0.781$, $A=0.109$, and $\sigma=1.684$\angs. Thus, the \suldiox~tends to locate just beneath the surface when in a low-concentration water environment, and it did not fall further into the bulk or move out of the surface into the gas phase. This surface active behavior was found experimentally by a previous SFG study by our group,\cite{Tarbuck2005,Tarbuck2006} and also verified by the computational simulations and spectral calculations of Dang et al.\cite{Baer2010} It was concluded that a surface \suldiox~hydrate complex forms and modifies the structure of water above the Gibbs dividing surface (GDS) shifting \wat~free-OH oscillators in towards the bulk, creating a stronger hydrogen-bonding network. In a later section of this article we look at the effect of \suldiox~on surface water orientation.

Both saturated \suldiox~surfaces exhibit accumulations of \suldiox. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox~that does not adsorb to the surface. The coefficient values for the top surface from eq \ref{eq:gaussian} are $\mu_{top}=2.695$, $A_{top}=7.001$, and $\sigma_{top}=3.203$. The bottom surface values are $\mu_{bottom}=-33.846$, $A_{bottom}=6.618$, and $\sigma_{bottom}=3.151$\angs. The added concentration of \suldiox~creates a layer of molecules adsorbed on top of the water surface. The center of this distribution is further into the gas phase than for the single-\suldiox~molecule surface. The accumulation of \suldiox~in this classical simulation coincides with the experimental conclusions of a surface of hydrate-complexed \suldiox, but without breakble bonds in the simulation the chemistry that may pull \suldiox~into the bulk water phase is absent. We have confidence in the surface complexation that is exhibited, the effect of the \suldiox~on the surface water molecules, and the accumulation of \suldiox at the interface. However, we do not yet conclude that the specific locations of \suldiox~on top of the water surface are as accurate as those found in the DFT ab initio calculations of Dang et al.\cite{Baer2010}

>>>>

In the neat-water \suldiox~distribution, $\mu=0.781$, $A=0.109$, and $\sigma=1.684$\angs. Thus, the \suldiox~has a surface affinity when in a low-concentration water environment, and it does not fall further into the bulk or move out of the surface into the gas phase. This surface active behavior was found experimentally by a previous SFG study by our group,\cite{Tarbuck2005,Tarbuck2006} and also verified by the computational simulations and spectral calculations of Dang et al.\cite{Baer2010} It was concluded that a surface \suldiox~hydrate complex forms and modifies the structure of water above the Gibbs dividing surface (GDS) shifting \wat~free-OH oscillators in towards the bulk, creating a stronger hydrogen-bonding network. In a later section of this article we look at the effect of \suldiox~on surface water orientation.

Both saturated \suldiox~surfaces exhibit accumulations of \suldiox. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox~that does not adsorb to the surface. The coefficient values for the top surface from eq \ref{eq:gaussian} are $\mu_{top}=2.695$, $A_{top}=7.001$, and $\sigma_{top}=3.203$. The bottom surface values are $\mu_{bottom}=-33.846$, $A_{bottom}=6.618$, and $\sigma_{bottom}=3.151$\angs. The added concentration of \suldiox~creates a layer of molecules adsorbed on top of the water surface. The center of this distribution is further into the gas phase than for the single-\suldiox~molecule surface. The accumulation of \suldiox~in this classical simulation coincides with the experimental conclusions of \suldiox~surface hydrate complex formation. However, without simulating breakble bonds the chemistry that may pull \suldiox~into the bulk water phase, and the subsequent reaction to form ions is absent. We have confidence in the surface complexation that is exhibited, the effect of the \suldiox~on the surface water molecules, and the accumulation of \suldiox at the interface. However, we do not yet conclude that the specific locations of \suldiox~on top of the water surface are as accurate as those found in the DFT ab initio calculations of Dang et al.\cite{Baer2010} As was pointed out in their computations, the classical potential does not reproduce the bonding of the first hydration shell around \suldiox, and so conclusions about specific complex formation or geometries are best made from the ab initio simulation results reported.
